\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                % set paper size to letterpaper. change to a4paper for resumes outside of North America
top=0.4in,                          % specify top page margin
bottom=0.4in,                       % specify bottom page margin
left=0.5in,                         % specify left page margin
right=0.5in]{geometry}              % specify right page margin

\usepackage{XCharter}               % set font. comment this line out if you want to use the default LaTeX font Computer Modern
\usepackage[T1]{fontenc}            % output encoding
\usepackage[utf8]{inputenc}         % input encoding
\usepackage{enumitem}               % enable lists for bullet points: itemize and \item
\usepackage{fontawesome}            % enable font awesome icons
\usepackage[hidelinks]{hyperref}    % format hyperlinks
\usepackage{titlesec}               % enable section title customization
\raggedright                        % disable text justification
\pagestyle{empty}                   % disable page numbering

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

% format section headings: bolding, size, white space above and below
\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

% format bullet points: size, white space above and below, white space between bullets
\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt, topsep=7pt} %%% Test various topsep values to fix vertical spacing errors

% resume starts here
\begin{document}

% name
\centerline{\Huge Evan Noronha}

\vspace{5pt}

% contact information
\centerline {\href{mailto:hello@evannoronha.com}{\faEnvelope \space hello@evannoronha.com} | \href{https://www.linkedin.com/in/evan-noronha/}{\faLinkedin \space evan-noronha} | \href{https://github.com/evannoronha}{\faGithub \space evannoronha}}

\vspace{-10pt}

% skills section
\section*{Skills}
\textbf{Languages:} Javascript/Typescript, C\#, Python, Java, SQL, PHP, HTML, CSS, Shell Scripting (Powershell, Bash) \\
\textbf{Tools:} Git, Linux, Docker + Kubernetes, .NET, Azure Devops, Github Actions, React, Azure, Cloudflare, AWS \\
\textbf{Skills:} Agile (Scrum, Kanban), DevOps, CI/CD, REST APIs, Microservices Architecture, Infrastructure as Code \\

\vspace{-6.5pt}

% experience section
\section*{Experience}
\textbf{Software Engineer II,} {Microsoft} -- Seattle, WA \hfill May 2022 -- Jan 2025 \\
\vspace{-9pt}
\begin{itemize}
  \item Developed, deployed and tested a virtualized satellite ground station for securely transmitting Earth observation data between Edge and Cloud environments.
  \item Led the transition away from deployments of bespoke resources to using automated rollout tooling with declarative infrastructure definitions using Bicep for Azure resources and Helm for containerized applications.
  \item Guided squad ceremonies as Scrum Master for a team of 5 developers over the course of six months, including sprint planning, standups, and retrospectives to build clarity and reach concensus on goals and deliverables.
  \item Designed and implemented a shared hosting environment for Azure Space teams to deploy productized software offerings while minimizing go-to-market time and duplication of work for service observability, secrets management, storage.
  \item Met 100\% of Azure cybersecurity and compliance requirements while respecting the responsibility for customers' most critical and sensitive workloads. Achieved this requirement through network isolation, appropriate secrets handling, and migrating from public to to internal package registries as needed.
\end{itemize}

\textbf{Software Engineer,} {iFixit} -- San Luis Obispo, CA \hfill Jan 2017 -- May 2022 \\
\vspace{-9pt}
\begin{itemize}
  \item Worked as a full-stack software development engineer. Main application runs on PHP 8.0 backed by MySQL serving over 1m requests / day. Development and deployment runs in a Linux environment (Fedora 32). \\
  \item Lead developer and interim project manager for B2B project implementing a part picker for 10K+ power tools. Cloud-based solution is used in every Home Depot Rental Center in the US and Canada. Project included on-site requirements gathering, regular check-ins with clients, and long-term support and monitoring. \\
  \item Transformed iFixit’s custom-built e-commerce solution into a service architecture that processes 500 orders/day with over \$1m in monthly revenue. Major project components included migrating customer and order management to Shopify and publishing product data via Akeneo + Algolia. \\
  \item Mentored incoming developers in organizational best practices to provide an introduction to software development. Engaged both in a one-on-one context through pair programming and code review, and also by presenting tech talks on tools and technolgies. \\
  \item Collaborated cross-functionally with founders, leadership and key stakeholders to define strategy and roadmap. \\
\end{itemize}

\textbf{Technical Writer,} {iFixit} -- San Luis Obispo, CA \hfill Mar 2015 -- May 2017 \\
\vspace{-9pt}
\begin{itemize}
  \item Disassembled consumer electronics and published teardowns to assess repairability and design choices. \\
  \item Documented troubleshooting and repair instructions for popular devices. This included developing and sharing best practices for disassembly, identifying parts with a high failure rate, and photographing repair procedures. \\
  \item Presented live teardowns at manufacturing and design trade shows. Spoke about Right to Repair and Planned Obsolescence, and performed live teardowns for industry professionals. \\
\end{itemize}

\textbf{Photographer and Web Developer,} {Orfalea College of Business} -- San Luis Obispo, CA \hfill Jan 2014 -- May 2015 \\
\vspace{-9pt}
\begin{itemize}
  \item Designed and maintained college websites, improving accessibility and usability for faculty and students. \\
  \item Produced high-quality photography for marketing and promotional materials. \\
\end{itemize}

\vspace{-18.5pt}

% % projects section
% \section*{Projects}
% \textbf{Personal Blog: https://hillpeople.net} \hfill \href{https://github.com/evannoronha/hillpeople}{\faGithub \space evannoronha/hillpeople} \\
% \vspace{-9pt}
% \begin{itemize}
%   \item A blog where my partner and I write about our adventures in the outdoors, travel, and life.
%   \item Built using AstroJS and hosted using Cloudflare Workers. Backed by Strapi CMS for content management.
% \end{itemize}

% \textbf{Alpenglow Guiding: https://alpenglowguiding.com} \hfill \href{https://github.com/evannoronha/alpenglowguiding}{\faGithub \space evannoroha/alpenglowguiding} \\
% \vspace{-9pt}
% \begin{itemize}
%   \item A website for
% \end{itemize}

% \vspace{-18.5pt}

% education section
\section*{Education}
\textbf{California Polytechnic State University}, San Luis Obispo, CA -- Computer Science \hfill 2013 - 2019

\end{document}
